Time Series Bootstrapping For Solar Current

### 2021-12-09 deliverables/paper.Rmd
Added Time Series Graphs
Added the graphs for blocks across different hour windows.

```{r sampling}
# B1 <- df[df$Hour == c(7:10),]$current_output # Hours before peak
# B2 <- df[df$Hour == c(11:14),]$current_output # Peak hours
# B3 <- df[df$Hour == c(15:18),]$current_output # Hours after peak

>>>>

```{r sampling}
time_series_irradiance <- function(df, variable, var_name, hour_range) {
  newdf <- df %>%
    mutate(date = lubridate::make_datetime(Year, Month, Day, Hour, Minute)) %>%
    # each day in this dataset is subset from 11:16, meaning there is 6 hours per day
    head(hour_range * 6)

  blocks <- c(newdf$date[seq(1,length(newdf$date), hour_range)])

  re_plot <- ggplot(newdf) +
    geom_line(aes_string(x = "date", y = variable)) +
    geom_vline(xintercept = blocks, colour = "red") +
    xlab("Date") +
    ylab(var_name) +
    theme_bw()
  return(ret_plot)
}

sixhr_plot_current <- time_series_irradiance(df_high_irradiance, "current_out", "Current Output", 6)
ggsave("./images/sixhr_plot_current.png", make_plot_for_pres(sixhr_plot_current))

HOUR_WINDOW <- 8:19
df_more_irradiance <- df[df$Hour %in% HOUR_WINDOW, ]
filtered_current_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$current_out)) +
  theme_bw()
print(filtered_current_hist)

twelvehr_plot_current <- time_series_irradiance(df_more_irradiance, "current_out", "Current Output", 12)
ggsave("./images/twelvehr_plot_current.png", make_plot_for_pres(twelvehr_plot_current))

day_plot_current <- time_series_irradiance(df, "current_out", "Current Output", 24)
ggsave("./images/day_plot_current.png", make_plot_for_pres(day_plot_current))

# B1 <- df[df$Hour == c(7:10),]$current_output # Hours before peak
# B2 <- df[df$Hour == c(11:14),]$current_output # Peak hours
# B3 <- df[df$Hour == c(15:18),]$current_output # Hours after peak
